% Created 2017-03-10 Fri 09:59
\documentclass[12pt]{amsart}
                        \usepackage[all]{pabmacros}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage[nointegrals]{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{hyperref}
\tolerance=1000
\usepackage{amsmath}
\usepackage[bibstyle=alphabetic,citestyle=alphabetic,backend=bibtex]{biblatex}
\makeatletter
\def\blx@maxline{77}
\makeatother
\bibliography{refs}
\AtEveryBibitem{\clearfield{doi}}
\AtEveryBibitem{\clearfield{url}}
\AtEveryBibitem{\clearfield{issn}}
\renewcommand*{\bibfont}{\footnotesize}
\date{}
\renewcommand*{\bibfont}{\footnotesize}
\author{Paul Bryan}
\date{}
\title{C8. Research Opportunity and Performance Evidence (ROPE) - Significant research outputs}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}

\usepackage{enumitem}
\usepackage{setspace}
\usepackage[margin = 6mm]{geometry}
\pagestyle{empty}

\begin{document}

\onehalfspacing

\maketitle

\section*{\textbf{Refereed Journal Articles}}
\label{sec-1}

\begin{enumerate}
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{Curvature bounds by isoperimetric comparison for normalized Ricci flow on the two-sphere}. Calc. Var. Partial Differential Equations 39, 419--428, 2010.
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{A comparison theorem for the isoperimetric profile under curve-shortening flow}. Comm. Anal. Geom. 19, 503--539, 2011.
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{Curvature bound for curve shortening flow via distance comparison and a direct proof of Grayson's theorem}. J. Reine Angew. Math. 653, 179--187. 2011.
\item * \textbf{Paul Bryan}. \emph{Isoperimetric Comparison Techniques for Low Dimension Curvature Flows}. Ph.D. Thesis, Australian National University, 2012.
\item * \textbf{Paul Bryan} \emph{Curvature bounds via an isoperimetric comparison for Ricci flow on surfaces} Ann. Scuola Norm. Sup. Pisa Cl. Sci September 2016, Volume 16, Issue 3
\item * \textbf{Paul Bryan}, Janelle Louie \emph{Classification of Convex Ancient Solutions to Curve Shortening Flow on the Sphere} J. Geom. Anal. April 2016, Volume 26, Issue 2, 858--872
\item * \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{Harnack inequalities for evolving hypersurfaces on the sphere} Comm. Anal Geom. (Accepted) 2016 arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1512.03374})
\item \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{A unified flow approach to smooth, even $L_p$-Minkowski problems}, Analysis \& PDE (Accepted) 2016 arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1512.03374})
\end{enumerate}

\section*{\textbf{Other Research Outputs}}
\label{sec-2}
\subsection*{Pre-prints}
\label{sec-2-1}

\begin{enumerate}[resume]
\item * \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{On the classification of ancient solutions to curvature flows on the sphere}, Submitted to \emph{Journal of the European Mathematical Society}, 2016. arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1604.01694})
\item * \textbf{Paul Bryan}, Mohammad Ivaki \emph{Harnack estimate for mean curvature flow on the sphere} Submitted to \emph{Journal of Differential Geometry}, 2015. arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1508.02821})
\end{enumerate}

\subsection*{Invited Talks}
\label{sec-2-2}
\begin{enumerate}[resume]
\item Dec 2016 \emph{Harnack Inequalities and Ancient Solutions of Hypersurface Flows} Singularities of Geometric Partial Differential Equations, Warwick University
\item Jun 2016 \emph{Ancient soutions and Harnack Inequalities for curvature flows} Pontifical Catholic University of Chile
\item May 2016 \emph{Ancient solutions of curvature flows in the sphere} University of Warwick
\item Nov 2015 \emph{Harnack inequalities, Aleksandrov reflection, and ancient solution of curvature flows on the sphere.}  Free University, Berlin
\item Oct 2015 \emph{Harnack inequalities and Classification of Ancient Solutions to Mean Curvature Flow.} Riemann Center, Liebniz University Oberseminar
\item Sep 2015 \emph{Isoperimetric Inequalities: What's new since Queen Dido? An case for the isoperimetric profile.} ANU Colloquium
\item Sep 2015 \emph{Harnack inequalities and Classification of Ancient Solutions to Mean Curvature Flow} Monash University Geometry and Analysis Seminar
\item Aug 2015 \emph{Harnack inequalities and Classification of Ancient Solutions to Mean Curvature Flow} ANU Geometry and Analysis Seminar
\item Jun 2015 \emph{Comparison results for the Isoperimetric profile and curvature flows} Columbia University Geometry Seminar
\item Apr 2015 \emph{A viscosity equation and applications of the maximum principle for the isoperimetric profile} Geometric Flows: Recent Developments and Applications (BIRS)
\item May 2014 \emph{A history of Isoperimetric Problems}. UCSC Colloquium.
\item March 2014 \emph{Isoperimetric Problems in Geometry}. UCI Geometry Seminar.
\item October 2013 \emph{Polar Dual of Convex Bodies and Curvature Flows}. UCSD Differential Geometry Seminar.
\item May 2013 \emph{Isoperimetry and Viscosity Solutions in Geometric Evolution Equations}. Pacific Northwest Geometry Seminar.
\item October 2012 \emph{Isoperimetric comparison techniques for Ricci flow on surfaces}. UCSD Differential Geometry Seminar.
\item Jun 2012 \emph{A Viscosity Equation for the Isoperimetric Profile of Surfaces}. Peking University, Analysis Seminar.
\item Sep 2011 \emph{An Isoperimetric Comparison Theorem for the Ricci Flow on Surfaces}. 55th Annual Australian Mathematical Society Meeting.
\item Aug 2011 \emph{An Isoperimetric Comparison Theorem for the Ricci Flow on Surfaces}. Peking University, Analysis Seminar.
\item Mar 2009 \emph{An Isoperimetric Comparison Theorem for the Ricci Flow on the $2$-sphere}. Workshop on Nonlinear Analysis, Australian National University.
\item Oct 2008 \emph{A Distance Comparison Theorem for the Curve Shortening Flow}. Workshop on Geometric Analysis, University of Wollongong.
\item Feb 2007 \emph{The Curve Shortening Flow: Grayson's Theorem}. AMSI/CSIRO The Big Day In.
\end{enumerate}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}
